Balsa: A Compact Line Notation Based on SMILES

### 2022-07-09 manuscript.tex
Adds figure for depth-first traversal. Closes #21
Adds figure for writing stack. Closes #22

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Depth-first traversal.}
    \label{fig:depth-first-traversal}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Stack for branch assembly.}
    \label{fig:branch-stack}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{depth-first-traversal.pdf}
    \caption{Depth-first traversal. Traversal of a disconnected, cyclic molecular graph (top) in depth-first order leads to a tree containing one bridge and one gap (bottom).}
    \label{fig:depth-first-traversal}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{stack-for-writer.pdf}
    \caption{Stack for writing strings. Traversal of the root atom (C) creates a new entry. Encountering the start of a branch (N, S) creates a new entry preceded by an open parenthesis symbol (\ttt{(}). Extending a branch writes to the top stack item (I, F, O). Closing a branch pops the top item then concatenates it, together with a close parenthesis symbol (\ttt{)}), to the new top item.}
    \label{fig:branch-stack}
\end{figure}
